Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
more comments on section 3

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.  Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
\begin{enumerate}
\item[(\ref{lem:relations_from_generators_induction}.1)]  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
\item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item[(\ref{lem:relations_from_generators_induction}.3)] All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	& S \\
	\cup \; &\langle T\rangle \\
	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
\end{align*}
\end{enumerate}
Then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose monomial $f\in T$ has a pole order $a$ at $P$.  Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{proof}

As suggested by the previous lemma, we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
\begin{defn}
We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff one of the following holds
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$
\item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative.  
\end{enumerate}
\end{defn}
We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is, Aaron: I suggest not to use the phrase ``leave as an exercise'' in a paper}
We now offer a lemma that allows us to inductively add $\mathbb{Q}$-points to a divisor and describe the new generators and relations.

>>>>

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m,$
and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
$R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively \todo{Usually respectively is applied when two things are said at the same time, this doesn't seem to fit the usual gramattical pattern}.  
Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
\begin{enumerate}
\item[(\ref{lem:relations_from_generators_induction}.1)] \todo{It would probably be clearer to just call these conditions 1,2,3 instead of 3.2.1...}  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
\item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item[(\ref{lem:relations_from_generators_induction}.3)] All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	S	\cup \; \langle T\rangle \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
\end{align*}
\end{enumerate}
Then,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
	+ \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose a monomial $f\in T$ has a pole order $a$ at $P$. Then, since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f = (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
\end{align*}
\todo{Aaron: I don't understand why this holds}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
\end{align*}
\todo{Aaron: Why can't the initial term lie in S?}
\todo{It might be helpful to say where you use conditions 1 2 and 3.}
\end{proof}

As suggested by the previous lemma, \todo{Reference the lemma, instead of using previous, since things might get moved around} we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma. \todo{Again, reference this}
\begin{defn}
We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff \todo{It's better not to use abbreviations like iff in papers. Also, usually in definitions, one uses if in place of iff.} one of the following holds
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$ \todo{Order at which point, in this line and the next}
\item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative. \todo{I do not understand what this means, maximal under what ordering? Also, }
\end{enumerate}
\end{defn}
We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is, Aaron: I suggest not to use the phrase ``leave as an exercise'' in a paper}
We now offer a lemma that allows us to inductively add $\mathbb{Q}$-points to a divisor and describe the new generators and relations.
